RadLib: a radiative heat transfer model library for CFD

### 2021-04-13 submissions/CPC_response_to_reviewers.md

	**Section 3 has been revised and extended to include more information on how users can include and interact with the RadLib library, including explicit references to example files that further illustrate usage of the library.**

	**TO DO: add discussion and/or documentation on how to add new property models**

4) The Planck-mean absorption coefficient included in RadLib is based on TNF workshop data (from 2003). According to the references cited, these are fairly old correlations. If the authors use these data, I am concerned that the model parameters and correlations used in RadLib for the PM model may be obsolete and inaccurate. Can the authors please comment on this?

	**The authors purposely chose the TNF workshop data for calculating Planck Mean absorption coefficients because it is one of the most common and widely used radiation models applied to turbulent combustion simulations, despite its age and limitations. Section 2.1 has been revised to include a more explicit dicsussion of why the TNF radiation model was chosen and concerns related to its relative age and limited applicability. Section 4 includes example cases that clearly demonstrate the deficiencies of the PM model compared to the other models included with RadLib, and some additional discussion is available there.**

@@

5) On page 13, the authors present a paragraph describing Figs. 2 and 3 - the comparison of various radiation property models present in RadLib in one-dimensional configurations. The comparisons are presented simply as observations without any explanation or reasoning why the models behave the way as seen in Fig. 2 and 3. If I understand correctly, the focus of the work presented here is not the comparison of the accuracy of the three models but to showcase the library. Therefore, these comparisons - specifically without any explanation of the results - may not be essential to the current manuscript, and can be shortened. These results do serve as descriptions of example cases provided in RadLib. On the same page, the authors say that "While ommitted [should be omitted] here for brevity, the implemented WSGG and RCSLW models give essentially identical results to those presented in [11, 14] such that these examples also serve as a validation of the implementation of the
models." The authors should avoid qualitative description such as "essentially identical" in the context of validation and present a quantitative (e.g., % error) metric wherever possible. A strong validation is important for programs like this.

**TO DO: decide on whether or not to keep example plots in the paper**

6) The computational cost tables for two cases show a significantly different trend, which the authors attribute to "additional overhead required in performing the calculations." Can the authors be more specific as to what these overheads may be? They say that they have neglected the initialization and input/output costs. Also, do these CPU times presented include the cost for the ray-tracing solver as well? Are the grids kept the same for all configurations?

	**Section 4.1 already includes details of the computational cost calculations presented in Figure 4. The left hand plot (a) refers to one million evaluations of the absorption coefficients directly, while the right hand plot (b) refers to the cost to evaluate Example S3, which, like all of the example cases described in the first paragraph of Section 4, includes the ray-tracing solver. The quoted sentence has been revised to specify that the ray-tracing solver is primarily responsible for the additional overhead. Grids are identical for each configuration. Note that the RadLib library does not generate or manipulate grids as it is not involved in the RTE solution. The ray-tracing solver used in the example cases is provided for convenience and demonstration purposes.**

@@

7) In line 53 on page 4, the authors claim to have CH4 property in RadLib but none of the validation cases contain CH4. Furthermore, for RCSLW, the refer to Pearson's work as a source for data of CO2, H2O, and CO without indicating the source data for CH4.

	**CH4 is present only in the PM model sourced from the TNF Workshop [3,5], which includes CH4 absorption coefficients because most of the TNF Workshop target flames are fueled by Ch4. In general, CH4 is not a significant radiatively participating species in combustion systems, but it is included for completeness.**

@@

MINOR:

1) It should be clarified that RadLib only provides radiation properties for non-scattering media.

	**This clarification has been made explicitly in Section 2 and now appears throughout the text where appropriate.**

@@

3) In Page 2, "In some cases, radiative gains or losses are small compared to other energy sources or heat transfer modes and radiation can be safely neglected, ... difficult to simulate accurately without a robust radiation model." Please provide some references to support these arguments.

	**References have been added throughout to bolster weakly supported arguments. Note that the quoted statement and related discussion has been moved to Section 5 due to unrelated revisions.**

4) Please explain all the symbols used in equations. For example, eta in Eqn. 1 (and subsequent equations), Eb  in Eqn. 11.

	**Text surrounding equations has been revised throughout to ensure explicit definitions of variables.**

### 2021-04-14 manuscript/manuscript.tex
Reviewer revisions. All non-technical comments have been addressed. See response to reviewers document.

\begin{small}
\noindent
{\em Program Title:} RadLib                                         \\
{\em CPC Library link to program files:} (to be added by Technical Editor) \\
{\em Developer's repository link:} https://github.com/BYUignite/radlib \\
{\em Code Ocean capsule:} https://codeocean.com/capsule/0997975/tree \\
{\em Licensing provisions(please choose one):} MIT \\
{\em Programming language:} C++, Python                                   \\
{\em Nature of problem(approx. 50-250 words):} \\
Radiation property models can be difficult to understand and implement, often requiring a high degree of specialization. This presents a problem for practitioners who wish to use/implement radiation models for which such models consitute only a small but important part of a larger simulation. Turbulent combustion simulations are one such example. Often, rudimentary assumptions are made and this can negatively impact results. \\
{\em Solution method(approx. 50-250 words):}\\
We provide an open source radiation property library that uses modern versioning build tools, including C++ and Python interfaces and examples demonstrating usage of the models. The library can be extended to other models and interfaces. \\ 
{\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
The library is intended to be used in Linux-like terminal applications.  
   \\

@@

The interfaces, solver, and examples included with the library serve to demonstrate its use and validate the implementation and results. Figure \ref{fig:flowchart} illustrates the basic structure use of the RadLib package within a generic example using the provided interfaces. The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular geometry. After creating a radiation object, users interact with RadLib through the \texttt{get\textunderscore k\textunderscore a()} function, which requires arguments corresponding to the system temperature; system pressure; species mass fractions for H$_2$O, CO$_2$, CO, and CH$_4$; soot volume fraction in units of parts per million (ppm), if applicable; and variables initialized to receive output values for the radiation absorption coefficients and their corresponding weights. For examples that illustrate how a user might interact with RadLib, refer to the \texttt{simple\textunderscore interface.cc} and \texttt{simple\textunderscore interface.py} example files located in the \texttt{examples/c++} and \texttt{examples/python} folders, respectively. 
%
\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
	\end{center}
	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
\label{fig:flowchart}
\end{figure}
%

@@

These cases are intended to illustrate the use of the RadLib library and are not exhaustive. Details about these examples and their motivations can be found in their respective references. While ommitted here for brevity, the implemented WSGG and RCSLW models give essentially identical results to those presented in \cite{Solovjov_2017,Bordbar_2020} such that these examples also serve as a validation of the implementation of the models.

@@

Figure~\ref{f:cost}b shows the cost to evaluate Example S3. 
In this case the costs of the models, relative to WSGG, is approximately 0.75, 1.1, 1.4, 1.9, and 2.9, for PM, and RCSLW with $n=1$, 2, 4, 8 gray gases, respectively. Here, the WSGG model took 0.0079 s. In running Example S3, the costs of the various models are much more similar than in evaluating gas properties alone due to the additional overhead required in performing the calculations. In the results presented, only the cost of evaluating the solution was included; initialization and input/output costs were neglected.

@@

@@

%Author guidelines for this section
%\begin{itemize}
% \item \textbf{This is the main section of the article and the reviewers weight the description here appropriately}
% \item Indicate in what way new research questions can be pursued as a result of the software (if any).
% \item Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).
% \item Indicate in what way the software has changed the daily practice of its users (if so).
% \item Indicate how widespread the use of the software is within and outside the intended user group.
% \item Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).
%\end{itemize}

@@

\bibliographystyle{elsarticle-num} 
%\bibliography{references}

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{Hottel_1967}
H.~Hottel, A.~Sarofim, Radiative Transfer, {McGraw-Hill}, New York, 1967.

\bibitem{Modest_2013}
M.~F. Modest, Radiative Heat Transfer, third edition, {Academic Press},
  New York, 2013.

\bibitem{Modest_2016}
M.~F. Modest, D.~C. Haworth, Radiative Heat Transfer in Turbulent Combustion Systems, {Springer}, New York, 2016.

\bibitem{Smith_2003}
N.~Smith, J.~Gore, J.~Kim, Q.~Tang,
  \href{https://tnfworkshop.org/radiation/}{{TNF} workshop radiation models}
  (2003).
\newline\urlprefix\url{https://tnfworkshop.org/radiation/}

\bibitem{Grosshandler_1993}
W.~L. Grosshandler, {RADCAL}: A narrow-band model for radiation calculations in
  a combustion environment: Nist technical note 1402.

\bibitem{Barlow_2001}
R.~S. Barlow, A.~N. Karpetis, J.~H. Frank, J.-Y. Chen, Scalar profiles and {NO}
  formation in laminar opposed-flow partially premixed methane/air flames,
  Combustion and Flame 127~(3) (2001) 2102--2118.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00313-3}
  {\path{doi:10.1016/S0010-2180(01)00313-3}}.

\bibitem{Barlow_1999}
R.~Barlow, N.~Smith, J.~Chen, R.~Bilger,
  \href{http://www.sciencedirect.com/science/article/pii/S0010218098000716}{Nitric
  oxide formation in dilute hydrogen jet flames: isolation of the effects of
  radiation and turbulence-chemistry submodels}, Combustion and Flame 117~(1-2)
  (1999) 4--31.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(98)00071-6}
  {\path{doi:10.1016/S0010-2180(98)00071-6}}.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218098000716}

\bibitem{Frank_2000}
J.~H. Frank, R.~S. Barlow, C.~Lundquist, Radiation and nitric oxide formation
  in turbulent non-premixed jet flames, Proceedings of the Combustion Institute
  28~(1) (2000) 447--454.
\newblock \href {http://dx.doi.org/10.1016/S0082-0784(00)80242-8}
  {\path{doi:10.1016/S0082-0784(00)80242-8}}.

\bibitem{Zhu_2002}
X.~Zhu, J.~Gore, A.~N. Karpetis, R.~S. Barlow,
  \href{http://www.sciencedirect.com/science/article/pii/S0010218002003413}{The
  effects of self-absorption of radiation on an opposed flow partially premixed
  flame}, Combustion and Flame 129~(3) (2002) 342--345.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(02)00341-3}
  {\path{doi:10.1016/S0010-2180(02)00341-3}}.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218002003413}

\bibitem{Coelho_2002}
P.~J. Coelho, O.~J. Teerling, D.~Roekaerts, Spectral radiative effects and
  turbulence-radiation-interaction in sandia flame {D}, in: {Barlow, Robert S.,
  Pope, Stephan B., Masri, Assaad R., Oefelein, Joseph C.} (Ed.), The
  Proceedings of the Sixth International Workshop on Measurement and
  Computation of Turbulent Nonpremixed Flames, 2002.

\bibitem{Bordbar_2014}
M.~H. Bordbar, G.~Wecel, T.~Hyppanen, A line by line based weighted sum of gray
  gases model for inhomogeneous {CO$_2$–H$_2$O} mixture in oxy-fired
  combustion, Combustion and Flame 161~(9) (2014) 2435--2445.
\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2014.03.013}
  {\path{doi:10.1016/j.combustflame.2014.03.013}}.

\bibitem{Bordbar_2020}
H.~Bordbar, G.~C. Fraga, S.~Hostikka,
  \href{http://www.sciencedirect.com/science/article/pii/S0735193319302660}{An
  extended weighted-sum-of-gray-gases model to account for all {CO$_2$-H$_2$O}
  molar fraction ratios in thermal radiation}, International Communications in
  Heat and Mass Transfer 110 (2020) 104400.
\newblock \href {http://dx.doi.org/10.1016/j.icheatmasstransfer.2019.104400}
  {\path{doi:10.1016/j.icheatmasstransfer.2019.104400}}.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0735193319302660}

\bibitem{Rothman_2010}
L.~S. Rothman, I.~E. Gordon, R.~J. Barber, H.~Dothe, R.~R. Gamache, A.~Goldman,
  V.~I. Perevalov, S.~A. Tashkun, J.~Tennyson,
  \href{http://www.sciencedirect.com/science/article/pii/S002240731000169X}{{HITEMP},
  the high-temperature molecular spectroscopic database}, Journal of
  Quantitative Spectroscopy {\&} Radiative Transfer 111~(15) (2010) 2139--2150.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.05.001}
  {\path{doi:10.1016/j.jqsrt.2010.05.001}}.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S002240731000169X}

\bibitem{Solovjov_2016}
V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The generalized {SLW}
  model, Journal of Physics: Conference Series 676 (2016) 1--36.

\bibitem{Solovjov_2017}
V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The rank correlated
  {SLW} model of gas radiation in non-uniform media, Journal of Quantitative
  Spectroscopy {\&} Radiative Transfer 197 (2017) 26--44.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2017.01.034}
  {\path{doi:10.1016/j.jqsrt.2017.01.034}}.

\bibitem{Badger_2019}
J.~Badger, B.~W. Webb, V.~P. Solovjov, An exploration of advanced {SLW}
  modeling approaches in comprehensive combustion predictions, Combustion
  Science and Technology 012022~(676) (2019) 1--17.
\newblock \href {http://dx.doi.org/10.1080/00102202.2019.1678907}
  {\path{doi:10.1080/00102202.2019.1678907}}.

\bibitem{Solovjov_2000}
V.~P. Solovjov, B.~W. Webb, {SLW} modeling of radiative transfer in
  multicomponent gas mixtures, Journal of Quantitative Spectroscopy and
  Radiative Transfer 65 (2000) 655--672.

\bibitem{Solovjov_2001}
V.~P. Solovjov, B.~W. Webb, An efficient method for modeling radiative transfer
  in multicomponent gas mixtures with soot, Transactions of the ASME 123 (2001)
  450--457.

\bibitem{Solovjov_2008}
V.~P. Solovjov, B.~W. Webb, Multilayer modeling of radiative transfer by {SLW}
  and {CW} methods in non-isothermal gaseous medium, Journal of Quantitative
  Spectroscopy and Radiative Transfer 109~(2) (2008) 245--257.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2007.08.015}
  {\path{doi:10.1016/j.jqsrt.2007.08.015}}.

\bibitem{Solovjov_2011}
V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, The {SLW}-1 model for efficient
  prediction of radiative transfer in high temperature gases, Journal of
  Quantitative Spectroscopy and Radiative Transfer 112~(7) (2011) 1205--1212.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.08.009}
  {\path{doi:10.1016/j.jqsrt.2010.08.009}}.

\bibitem{Solovjov_2014}
V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, Extension of the exact {SLW} model to
  non-isothermal gaseous media, Journal of Quantitative Spectroscopy and
  Radiative Transfer 143 (2014) 83--91.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2013.10.008}
  {\path{doi:10.1016/j.jqsrt.2013.10.008}}.

\bibitem{Webb_2018}
B.~W. Webb, V.~P. Solovjov, F.~Andr{\'e}, An exploration of the influence of
  spectral model parameters on the accuracy of the rank correlated slw model,
  Journal of Quantitative Spectroscopy and Radiative Transfer 218 (2018)
  161--170.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2018.06.023}
  {\path{doi:10.1016/j.jqsrt.2018.06.023}}.

\bibitem{Pearson_2014}
J.~Pearson, B.~Webb, S.~V.P., J.~Ma, Efficient representation of the absorption
  line blackbody distribution function for {H$_2$O}, {CO$_2$}, and {CO} at
  variable temperature, mole fraction, and total pressure, Journal of
  Quantitative Spectrosopy and Radiative Transfer 138 (2014) 82--96.

\bibitem{Brewster_1992}
M.~Q. Brewster, Thermal Radiative Transfer and Properties, Wiley, 1992.

\bibitem{Lee_1981}
S.~C. Lee, C.~L. Tien, Optical constants of soot in hydrocarbon flames,
  Symposium (International) on Combustion 18~(1) (1981) 1159--1166.
\newblock \href {http://dx.doi.org/10.1016/S0082-0784(81)80120-8}
  {\path{doi:10.1016/S0082-0784(81)80120-8}}.

\bibitem{Stull_1960}
V.~R. Stull, G.~N. Plass, Emissivity of dispersed carbon particles, Journal of
  the Optical Society of America 50~(2) (1960) 121.
\newblock \href {http://dx.doi.org/10.1364/JOSA.50.000121}
  {\path{doi:10.1364/JOSA.50.000121}}.

\bibitem{Dalzell_1969}
W.~H. Dalzell, A.~F. Sarofim, Optical constants of soot and their application
  to heat-flux calculations, Journal of Heat Transfer 91~(1) (1969) 100--104.
\newblock \href {http://dx.doi.org/10.1115/1.3580063}
  {\path{doi:10.1115/1.3580063}}.

\bibitem{Howarth_1966}
C.~R. Howarth, P.~J. Foster, M.~W. Thring (Eds.), The Effect of Temperature on
  the Extinction of Radiation By Soot Particles, Begellhouse, 1966.
\newblock \href {http://dx.doi.org/10.1615/IHTC3.1210}
  {\path{doi:10.1615/IHTC3.1210}}.

\bibitem{Chang_1990}
H.-c. Chang, T.~T. Charalampopoulos, Determination of the wavelength dependence
  of refractive indices of flame soot, Proceedings of the Royal Society of
  London. Series A: Mathematical and Physical Sciences 430~(1880) (1990)
  577--591.
\newblock \href {http://dx.doi.org/10.1098/rspa.1990.0107}
  {\path{doi:10.1098/rspa.1990.0107}}.

\bibitem{Felske_1984}
J.~D. Felske, T.~T. Charalampopoulos, H.~S. Hura, Determination of the
  refractive indices of soot particles from the reflectivities of compressed
  soot pellets, Combustion Science and Technology 37~(5-6) (1984) 263--283.
\newblock \href {http://dx.doi.org/10.1080/00102208408923757}
  {\path{doi:10.1080/00102208408923757}}.

>>>>

\begin{small}
\noindent
{\em Program Title:} RadLib                                         \\
{\em CPC Library link to program files:} (to be added by Technical Editor) \\
{\em Developer's repository link:} https://github.com/BYUignite/radlib \\
{\em Code Ocean capsule:} https://codeocean.com/capsule/0997975/tree \\
{\em Licensing provisions(please choose one):} MIT \\
{\em Programming language:} C++, Python                                   \\
{\em Nature of problem(approx. 50-250 words):} \\
Radiative heat transfer in combustion CFD problems is typically neglected or oversimplified, resulting in significant error and inaccuracy in combustion simulations. Radiation modeling, however, often requires a high degree of specialization due to its complexity and the challenges associated with implementation in existing CFD codes, which presents a substantial obstacle to researchers who wish to address the inaccuracies introduced by insufficient radiative heat transfer modeling in combustion simulations. \\
{\em Solution method(approx. 50-250 words):}\\
We present RadLib, an open-source C++ library of validated radiation property models that can be applied alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for combustion CFD. The package includes multiple interface options (C++ and Python), several illustrative examples with a provided ray-tracing solver, and a framework for expansion to include additional radiation property models and interfaces.\\ 
{\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
The library is intended to be used in Linux-like terminal applications.  
   \\

@@

The interfaces, solver, and examples included with the library serve to demonstrate its use and validate the implementation and results. Figure \ref{fig:flowchart} illustrates the basic structure use of the RadLib package within a generic example using the provided interfaces. The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular geometry. After creating a radiation object, users interact with RadLib through the \texttt{get\textunderscore k\textunderscore a()} function, which requires arguments corresponding to the system temperature; system pressure; species mass fractions for H$_2$O, CO$_2$, CO, and CH$_4$; soot volume fraction in units of parts per million (ppm), if applicable; and variables initialized to receive output values for the radiation absorption coefficients and their corresponding weights. For examples that illustrate how a user might interact with RadLib, refer to the \texttt{simple\textunderscore interface.cc} and \texttt{simple\textunderscore interface.py} example files located in the \texttt{examples/c++} and \texttt{examples/python} folders, respectively. For information about adding additional radiative property models to the RadLib library, please refer to the package documentation. 
%
\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
	\end{center}
	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
\label{fig:flowchart}
\end{figure}
%

@@

These cases are intended to illustrate the use of the RadLib library and are not exhaustive. Details about these examples and their motivations can be found in their respective references. 
%TO DO address this:
While ommitted here for brevity, the implemented WSGG and RCSLW models give essentially identical results to those presented in \cite{Solovjov_2017,Bordbar_2020} such that these examples also serve as a validation of the implementation of the models.

@@

@@

%Note that we are presenting and not evaluating the models and make no claims as to causes of the results presented in the previous section. Several of the example cases deviate from the expected behavior (i.e. S2, S4). Also note that the PM and WSGG models are mostly empirical and contain very little representative physics, which can cause them to behave unpredictably in parameter ranges outside of those for which the models were specifically developed. If we look at Bordbar's paper, WSGG looks really good, but Example S4 gives us behavior we don't expect---WSGG performs very poorly. We don't know why, and we don't intend to explain it, but this is a good illustration of the fact that sometimes models need to be tested independently before application to a specific project. Sometimes a model that seems perfect may not be for your case, and RadLib is a good tool for investigating things like that.

@@

Figure~\ref{f:cost}b shows the cost to evaluate Example S3. 
In this case the costs of the models, relative to WSGG, is approximately 0.75, 1.1, 1.4, 1.9, and 2.9, for PM, and RCSLW with $n=1$, 2, 4, 8 gray gases, respectively. Here, the WSGG model took 0.0079 s. In running Example S3, the costs of the various models are much more similar than in evaluating gas properties alone due to the additional overhead of the ray-tracing solver in performing the calculations. In the results presented, only the cost of evaluating the solution was included; initialization and input/output costs were neglected.

@@

\bibliographystyle{elsarticle-num} 
\bibliography{references}

%\begin{thebibliography}{10}
%\expandafter\ifx\csname url\endcsname\relax
%  \def\url#1{\texttt{#1}}\fi
%\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
%\expandafter\ifx\csname href\endcsname\relax
%  \def\href#1#2{#2} \def\path#1{#1}\fi
%
%\bibitem{Hottel_1967}
%H.~Hottel, A.~Sarofim, Radiative Transfer, {McGraw-Hill}, New York, 1967.
%
%\bibitem{Modest_2013}
%M.~F. Modest, Radiative Heat Transfer, third edition, {Academic Press},
%  New York, 2013.
%  
%\bibitem{Modest_2016}
%M.~F. Modest, D.~C. Haworth, Radiative Heat Transfer in Turbulent Combustion Systems, {Springer}, New York, 2016.
%
%\bibitem{Smith_2003}
%N.~Smith, J.~Gore, J.~Kim, Q.~Tang,
%  \href{https://tnfworkshop.org/radiation/}{{TNF} workshop radiation models}
%  (2003).
%\newline\urlprefix\url{https://tnfworkshop.org/radiation/}
%
%\bibitem{Grosshandler_1993}
%W.~L. Grosshandler, {RADCAL}: A narrow-band model for radiation calculations in
%  a combustion environment: Nist technical note 1402.
%
%\bibitem{Barlow_2001}
%R.~S. Barlow, A.~N. Karpetis, J.~H. Frank, J.-Y. Chen, Scalar profiles and {NO}
%  formation in laminar opposed-flow partially premixed methane/air flames,
%  Combustion and Flame 127~(3) (2001) 2102--2118.
%\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00313-3}
%  {\path{doi:10.1016/S0010-2180(01)00313-3}}.
%
%\bibitem{Barlow_1999}
%R.~Barlow, N.~Smith, J.~Chen, R.~Bilger,
%  \href{http://www.sciencedirect.com/science/article/pii/S0010218098000716}{Nitric
%  oxide formation in dilute hydrogen jet flames: isolation of the effects of
%  radiation and turbulence-chemistry submodels}, Combustion and Flame 117~(1-2)
%  (1999) 4--31.
%\newblock \href {http://dx.doi.org/10.1016/S0010-2180(98)00071-6}
%  {\path{doi:10.1016/S0010-2180(98)00071-6}}.
%\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218098000716}
%
%\bibitem{Frank_2000}
%J.~H. Frank, R.~S. Barlow, C.~Lundquist, Radiation and nitric oxide formation
%  in turbulent non-premixed jet flames, Proceedings of the Combustion Institute
%  28~(1) (2000) 447--454.
%\newblock \href {http://dx.doi.org/10.1016/S0082-0784(00)80242-8}
%  {\path{doi:10.1016/S0082-0784(00)80242-8}}.
%
%\bibitem{Zhu_2002}
%X.~Zhu, J.~Gore, A.~N. Karpetis, R.~S. Barlow,
%  \href{http://www.sciencedirect.com/science/article/pii/S0010218002003413}{The
%  effects of self-absorption of radiation on an opposed flow partially premixed
%  flame}, Combustion and Flame 129~(3) (2002) 342--345.
%\newblock \href {http://dx.doi.org/10.1016/S0010-2180(02)00341-3}
%  {\path{doi:10.1016/S0010-2180(02)00341-3}}.
%\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218002003413}
%
%\bibitem{Coelho_2002}
%P.~J. Coelho, O.~J. Teerling, D.~Roekaerts, Spectral radiative effects and
%  turbulence-radiation-interaction in sandia flame {D}, in: {Barlow, Robert S.,
%  Pope, Stephan B., Masri, Assaad R., Oefelein, Joseph C.} (Ed.), The
%  Proceedings of the Sixth International Workshop on Measurement and
%  Computation of Turbulent Nonpremixed Flames, 2002.
%
%\bibitem{Bordbar_2014}
%M.~H. Bordbar, G.~Wecel, T.~Hyppanen, A line by line based weighted sum of gray
%  gases model for inhomogeneous {CO$_2$–H$_2$O} mixture in oxy-fired
%  combustion, Combustion and Flame 161~(9) (2014) 2435--2445.
%\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2014.03.013}
%  {\path{doi:10.1016/j.combustflame.2014.03.013}}.
%
%\bibitem{Bordbar_2020}
%H.~Bordbar, G.~C. Fraga, S.~Hostikka,
%  \href{http://www.sciencedirect.com/science/article/pii/S0735193319302660}{An
%  extended weighted-sum-of-gray-gases model to account for all {CO$_2$-H$_2$O}
%  molar fraction ratios in thermal radiation}, International Communications in
%  Heat and Mass Transfer 110 (2020) 104400.
%\newblock \href {http://dx.doi.org/10.1016/j.icheatmasstransfer.2019.104400}
%  {\path{doi:10.1016/j.icheatmasstransfer.2019.104400}}.
%\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0735193319302660}
%
%\bibitem{Rothman_2010}
%L.~S. Rothman, I.~E. Gordon, R.~J. Barber, H.~Dothe, R.~R. Gamache, A.~Goldman,
%  V.~I. Perevalov, S.~A. Tashkun, J.~Tennyson,
%  \href{http://www.sciencedirect.com/science/article/pii/S002240731000169X}{{HITEMP},
%  the high-temperature molecular spectroscopic database}, Journal of
%  Quantitative Spectroscopy {\&} Radiative Transfer 111~(15) (2010) 2139--2150.
%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.05.001}
%  {\path{doi:10.1016/j.jqsrt.2010.05.001}}.
%\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S002240731000169X}
%
%\bibitem{Solovjov_2016}
%V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The generalized {SLW}
%  model, Journal of Physics: Conference Series 676 (2016) 1--36.
%
%\bibitem{Solovjov_2017}
%V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The rank correlated
%  {SLW} model of gas radiation in non-uniform media, Journal of Quantitative
%  Spectroscopy {\&} Radiative Transfer 197 (2017) 26--44.
%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2017.01.034}
%  {\path{doi:10.1016/j.jqsrt.2017.01.034}}.
%
%\bibitem{Badger_2019}
%J.~Badger, B.~W. Webb, V.~P. Solovjov, An exploration of advanced {SLW}
%  modeling approaches in comprehensive combustion predictions, Combustion
%  Science and Technology 012022~(676) (2019) 1--17.
%\newblock \href {http://dx.doi.org/10.1080/00102202.2019.1678907}
%  {\path{doi:10.1080/00102202.2019.1678907}}.
%
%\bibitem{Solovjov_2000}
%V.~P. Solovjov, B.~W. Webb, {SLW} modeling of radiative transfer in
%  multicomponent gas mixtures, Journal of Quantitative Spectroscopy and
%  Radiative Transfer 65 (2000) 655--672.
%
%\bibitem{Solovjov_2001}
%V.~P. Solovjov, B.~W. Webb, An efficient method for modeling radiative transfer
%  in multicomponent gas mixtures with soot, Transactions of the ASME 123 (2001)
%  450--457.
%
%\bibitem{Solovjov_2008}
%V.~P. Solovjov, B.~W. Webb, Multilayer modeling of radiative transfer by {SLW}
%  and {CW} methods in non-isothermal gaseous medium, Journal of Quantitative
%  Spectroscopy and Radiative Transfer 109~(2) (2008) 245--257.
%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2007.08.015}
%  {\path{doi:10.1016/j.jqsrt.2007.08.015}}.
%
%\bibitem{Solovjov_2011}
%V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, The {SLW}-1 model for efficient
%  prediction of radiative transfer in high temperature gases, Journal of
%  Quantitative Spectroscopy and Radiative Transfer 112~(7) (2011) 1205--1212.
%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.08.009}
%  {\path{doi:10.1016/j.jqsrt.2010.08.009}}.
%
%\bibitem{Solovjov_2014}
%V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, Extension of the exact {SLW} model to
%  non-isothermal gaseous media, Journal of Quantitative Spectroscopy and
%  Radiative Transfer 143 (2014) 83--91.
%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2013.10.008}
%  {\path{doi:10.1016/j.jqsrt.2013.10.008}}.
%
%\bibitem{Webb_2018}
%B.~W. Webb, V.~P. Solovjov, F.~Andr{\'e}, An exploration of the influence of
%  spectral model parameters on the accuracy of the rank correlated slw model,
%  Journal of Quantitative Spectroscopy and Radiative Transfer 218 (2018)
%  161--170.
%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2018.06.023}
%  {\path{doi:10.1016/j.jqsrt.2018.06.023}}.
%
%\bibitem{Pearson_2014}
%J.~Pearson, B.~Webb, S.~V.P., J.~Ma, Efficient representation of the absorption
%  line blackbody distribution function for {H$_2$O}, {CO$_2$}, and {CO} at
%  variable temperature, mole fraction, and total pressure, Journal of
%  Quantitative Spectrosopy and Radiative Transfer 138 (2014) 82--96.
%
%\bibitem{Brewster_1992}
%M.~Q. Brewster, Thermal Radiative Transfer and Properties, Wiley, 1992.
%
%\bibitem{Lee_1981}
%S.~C. Lee, C.~L. Tien, Optical constants of soot in hydrocarbon flames,
%  Symposium (International) on Combustion 18~(1) (1981) 1159--1166.
%\newblock \href {http://dx.doi.org/10.1016/S0082-0784(81)80120-8}
%  {\path{doi:10.1016/S0082-0784(81)80120-8}}.
%
%\bibitem{Stull_1960}
%V.~R. Stull, G.~N. Plass, Emissivity of dispersed carbon particles, Journal of
%  the Optical Society of America 50~(2) (1960) 121.
%\newblock \href {http://dx.doi.org/10.1364/JOSA.50.000121}
%  {\path{doi:10.1364/JOSA.50.000121}}.
%
%\bibitem{Dalzell_1969}
%W.~H. Dalzell, A.~F. Sarofim, Optical constants of soot and their application
%  to heat-flux calculations, Journal of Heat Transfer 91~(1) (1969) 100--104.
%\newblock \href {http://dx.doi.org/10.1115/1.3580063}
%  {\path{doi:10.1115/1.3580063}}.
%
%\bibitem{Howarth_1966}
%C.~R. Howarth, P.~J. Foster, M.~W. Thring (Eds.), The Effect of Temperature on
%  the Extinction of Radiation By Soot Particles, Begellhouse, 1966.
%\newblock \href {http://dx.doi.org/10.1615/IHTC3.1210}
%  {\path{doi:10.1615/IHTC3.1210}}.
%
%\bibitem{Chang_1990}
%H.-c. Chang, T.~T. Charalampopoulos, Determination of the wavelength dependence
%  of refractive indices of flame soot, Proceedings of the Royal Society of
%  London. Series A: Mathematical and Physical Sciences 430~(1880) (1990)
%  577--591.
%\newblock \href {http://dx.doi.org/10.1098/rspa.1990.0107}
%  {\path{doi:10.1098/rspa.1990.0107}}.
%
%\bibitem{Felske_1984}
%J.~D. Felske, T.~T. Charalampopoulos, H.~S. Hura, Determination of the
%  refractive indices of soot particles from the reflectivities of compressed
